Model Checking Differentially Private Properties

### 2018-01-31 proof.tex
notations

 For the other direction, assume that all $\eta\in\Sigma^*$ it holds $v_{s_0}\cdot M(\eta)\cdot (v_B)^c \leq 0$. We prove by contradiction. Assume that $s_0\not\models \dpriv{1}{0} (F at_B)$. Since the relation $N_S$ contains only one pair, it implies that there exists a query scheduler $\scheduler{Q}\in\Sigma^\omega$ such that $\myPr{s_0}{M_{\scheduler{Q}}}{\neighbor{S}}{F at_B} >0$. It is then easy to construct a finite sequence $\eta\in\Sigma^*$ with  $v_{s_0}\cdot M(\eta)\cdot (v_B)^c > 0$, a contradiction.
\end{proof}

>>>>

 For the other direction, assume that all $\eta\in\Sigma^*$ it holds $v_{s_0}\cdot M(\eta)\cdot (v_B)^c \leq 0$. We prove by contradiction. Assume that $s_0\not\models \dpriv{1}{0} (F at_B)$. Since the relation $N_S=\{(s_0,s_0'),(s_0',s_0)\}$, there exists $(s_0,s_0')$,
  and a query scheduler $\scheduler{Q}\in\Sigma^\omega$ such that 
 \[
 \myPr{s_0}{M_{\scheduler{Q}}}{\neighbor{S}}{F at_B} \not\leq
  e \cdot
  \myPr{s_0'}{M_{\scheduler{Q}}}{\neighbor{S}}{F at_B}
 \]
 which implies $\myPr{s_0}{M_{\scheduler{Q}}}{\neighbor{S}}{F at_B} >0$. It is then easy to construct a finite sequence $\eta\in\Sigma^*$ with  $v_{s_0}\cdot M(\eta)\cdot (v_B)^c > 0$, a contradiction.
\end{proof}

### 2018-01-31 specifications.tex
notations

As an example, for our threshold model (Algorithm~\ref{algorithm:online-model}), we consider the property $\Phi=\wedge_{i=1}^{6} \dpriv{3}{0}(\X^i \top) \wedge \PJ{\le 0.025}(\X^6 F \top) \wedge \dpriv{3}{0.025}(\X^6 F \top)$, to express the privacy. The state $s_{34}$ (with the input threshold $t=3$, and the database $d=4$) satisfies $\Phi$ by our computation. It means the probability of reaching $\top$  within $i$ steps with $i$ ranges over $\{1,\ldots,6\}$, is $(3, 0)$-differentially private for the database $d$ and its neighbours ($d=3$ and $d=5$). It also states that the probability of reaching $\top$ after no less than $6$ steps, is smaller than $0.025$ and is  $(3, 0.025)$-differentially private.

@@

Consider the Bluetooth example in~\cite{DKNP04} and the
formula $\dpriv{\epsilon}{\delta}{\F \G \mathit{timeout}}$. Let us say
two states are neighbors if a slave device in a state is replaced by
another device in the other state.
Then the formula holds if the probability of having
continuous time out (say, in the denial of service attack) is
$(\epsilon, \delta)$-close for all neighbors. That is, adding a slave
device cannot increase the chance of service failure significantly.

>>>>

As an example, for our threshold model (Algorithm~\ref{algorithm:online-model}), we consider the property $\Phi=\wedge_{i=1}^{6} \dpriv{3}{0}(\X^i \top) \wedge \PJ{\le 0.025}(\X^6 F \top) \wedge \dpriv{3}{0.025}(\X^6 F \top)$, to express the privacy. The state $s_{34}$ (with the input threshold $t=3$, and the database $d=4$) satisfies $\Phi$ by our computation. It means the probability of reaching $\top$ at $i$ steps with $i$ ranges over $\{1,\ldots,6\}$, is $(3, 0)$-differentially private for the database $d$ and its neighbours ($d=3$ and $d=5$). It also states that the probability of reaching $\top$ after no less than $6$ steps, is smaller than $0.025$ and is  $(3, 0.025)$-differentially private.

@@

Consider the Bluetooth example in~\cite{DKNP04} and the
formula $\dpriv{\epsilon}{\delta}{\F \G \mathit{timeout}}$. Let us say
two states are neighbors if a slave device in a state is replaced by
another device in the other state.
Then the formula holds if the probability of having
continuous time out (say, in the denial of service attack) is
$(\epsilon, \delta)$-close for all neighbors. That is, replacing a slave
device cannot increase the chance of service failure significantly.
